---
title: "R Notebook"
output: html_notebook
---

Assignment 4 :  Logistic regression

Installing packages
```{r warning=FALSE, include=FALSE}
install.packages("tidyverse")
library(tidyverse)
install.packages("psych")
library(psych)
install.packages("magrittr")
library(magrittr)
install.packages("knitr")
library(knitr)
install.packages("haven")
library(haven)
install.packages("readxl")
library(readxl)
install.packages("stringi")
library(stringi)
```


Questions 1 and 2- leaving for now

Question 3
lineuptpta (binary, coding whether the target/perpetrator was present or absent in the lineup) 

lineupacc   (binary – the outcome variable – recording accuracy of decision in lineup task (1 = correct (hit in target present lineup, correct rejection in target present lineup)) 

videocondition  (binary, recording whether participants saw a long, or short video of the crime in question – about 3s vs 90s). 

confidenceresp  (continuous, witness’ self-reported confidence in the correctness of his/her decision, 0 to 100 point scale) 

lineuprt  (continuous, reaction time of witness in milliseconds in lineup task) 

decisionstrategyresp.1  (self-report item recording whether the witness made the decision after much deliberation, or ‘automatically’) 

decisionstrategyresp.2 (self-report item recording whether the witness rejected the lineup because the faces were unlike that of the perpetrator)


load data
```{r}
test.data <- load("eye_FR_testdata-1.txt")
train.data <- load("eye_FR_traindata-1.txt")
```

recoding variables
```{r}
traindata$lineupacc <- as.factor(traindata$lineupacc)
traindata$automatic<- as.factor(traindata$automatic) #likert strategies
traindata$facecomparison<- as.factor(traindata$facecomparison)
```

tpta
exposure
stategy

think, if memory is good and probe there- very automatic (4/5), if memory is good but not there- what happens then- searching...

main outcome is accuracy (o or 1)
boxplots -accuracy 
```{r}

```

describe by summary statistics
```{r}

```


building ordinal logistics model using train data
```{r}
model1 <-glm(lineupacc ~ lineuptpta + lineupacc + exposure + confidence + lineuprt + automatic + facecomparison, family = "binomial", data = traindata)

```



```{r}
predictdf <- data.frame(tobacco = 20)
predict(chdtobacco,newdata = 	predictdf) # to get the answer in logits
predict(chdtobacco,newdata = predictdf,type = “response”) # to get the answer in probabilities
x <- predict(chdtobacco,newdata=predictdf, 	type = “response”)
odds <- x/(1-x)  
```

